\myTitle

### 2024-04-17 tex/body-text-of-paper.tex
Added sentence to Discussion
More discussion additions.

When, and if, sequencing costs drop sufficiently, it may be possible to include
all different populations of a single species within a single standardized reference baseline
that performs equally well at broad and regional scales. A statistical approach for population
assignment from low coverage whole genome sequences appeared recently
\citep{desaixINPRESSpopulation}, and its authors noted that such a data type could
be ideal for producing reference baselines simultaneously applicable to broad scale
coverage and high resolution within sub-regions.   For the present, however,
baselines tailored to specific regions are essential for regional management questions.
It should be noted that recent

>>>>

We describe a novel panel of microhaplotype genetic markers for Chinook salmon 
in California that includes multiallelic gene regions with high variability for 
relationship inference and gene regions identified in whole-genome sequence data 
for increased power for population identification. We show how this set of markers
provides sufficient power for highly accurate identification of parent and offspring
pairs and full siblings in California Chinook salmon, and also allows near-perfect 
identification of individuals to population of origin. 
When, and if, sequencing costs drop sufficiently, it may be possible to include
all different populations of a single species within a single standardized reference baseline
that performs equally well at broad and regional scales. A statistical approach for population
assignment from low coverage whole genome sequences appeared recently
\citep{desaixINPRESSpopulation}, and its authors noted that such a data type could
be ideal for producing reference baselines simultaneously applicable to broad scale
coverage and high resolution within sub-regions.   For the present, however,
baselines tailored to specific regions are essential for regional management questions.
It should be noted that recent
